
#### Countries with clinical guidelines for healthcare workers on diagnosis and clinical management of cases and severe cases of _Aedes_-borne arboviral diseases (ref Q21)

```{r}
responses <- get_responses("21")
responses <- cbind(Country=data$SI01, responses) 

available <- responses$Country[which(responses$Response == "Yes")]
no_answer <- responses$Country[which(is.na(responses$Response))]
no_guidelines <- responses$Country[which(responses$Response == "No")]

```

The following countries indicated availability of clinical guidelines: `r available`.

`r no_answer` did not answer the question and `r no_guidelines` indicated no guidelines. 

<br> 

#### Training for healthcare workers on clinical diagnosis and management of _Aedes_-borne arboviral diseases (ref Q24)

```{r}
responses <- get_responses("24")
colnames(responses) <- c("Response","Training")
cbind(Country=data$SI01, responses) %>%
  mutate( Response = recode_factor(.x = Response,
                                   "Yes, specific training is provided. If so, please specify:"="X",
                                   "No"=" ")) %>%
  filter(Response=="X") %>% 
  select(-Response) %>%
  replace_na( list(Training="Not specified")) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()
```
