
```{r}
amro <- params$region == "AMRO"
```

#### National arboviral disease program notifications to the public about local transmission risk and/or possible vector-control activities as a prevention message for arboviral diseases within the last 2 years during outbreak (O) and non-outbreak (N) periods (ref Q44) 

```{r eval = !amro}
responses <- get_responses("44")
idx <- which( grepl("non-outbreak", colnames(responses)))

outbreaks <- cbind( Country=data$SI01, responses[,-idx]) %>%
  pivot_longer(!Country) 
new_cols <- matrix( unlist( strsplit(outbreaks$name, "\\]\\[") ), ncol=2, byrow=T)
outbreaks <- outbreaks %>% 
	mutate(Level = new_cols[,1], Response = new_cols[,2]) %>% 
	select(-name) %>%
	mutate( value = case_when( value == 1 ~ "O", value == 0 ~ "", is.na(value) ~ "")) %>%
	pivot_wider(names_from=Response, values_from=value) %>%
  select(-Level) 

non_outbreaks <- cbind( Country=data$SI01, responses[,idx]) %>%
  pivot_longer(!Country) 
new_cols <- matrix( unlist( strsplit(non_outbreaks$name, "\\]\\[") ), ncol=2, byrow=T)
non_outbreaks <- non_outbreaks %>% 
	mutate(Level = new_cols[,1], Response = new_cols[,2]) %>% 
	select(-name) %>%
	mutate( value = case_when( value == 1 ~ "N", value == 0 ~ "", is.na(value) ~ "")) %>%
	pivot_wider(names_from=Response, values_from=value) %>%
  select(-Level) 

responses <- left_join( outbreaks, non_outbreaks, by="Country") %>%
  unite( "Issued by national public health agency", c("Issued by national public health agency.x", "Issued by national public health agency.y"), sep="") %>%
  unite( "Issued by state/local health agencies", c("Issued by state/local health agencies.x", "Issued by state/local health agencies.y"), sep="") %>%
  unite( "No risk in the past two years", c("No risk in the past two years.x", "No risk in the past two years.y"), sep="" ) %>%
  unite("No notifications even though risk was present", c("No notifications even though risk was present.x", "No notifications even though risk was present.y"), sep="") %>% 
  mutate( across(everything(), str_replace, pattern="ON", replacement="O, N")) %>%
  mutate( across( everything(), na_if, "" ))

keep_cols = c()
for(i in 2:ncol(responses)){
  if( any( !is.na(responses[,i]) )){
    keep_cols = c(keep_cols, colnames(responses)[i])
  }
}

responses %>%
  select( c("Country",keep_cols) ) %>%
  # filter( if_any(keep_cols, ~ !is.na(.) ) ) %>%  ## uncomment to remove empty rows!
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  valign( valign = "top", part="header" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()
```

<br>

#### Media and other communication channels used for community sensitization, mobilisation and acceptance of interventions (ref Q44b)

```{r eval = !amro}
responses <- get_responses("44b")
other <- responses %>% select(Other)
responses <- responses %>% select(-Other)

responses <- responses %>%
  mutate_at( .vars=vars(colnames(responses)),
             .funs = forcats::fct_recode,
             "X" = "Yes",
             " " = "Not selected")

if( any(!is.na(other$Other))){
  responses <- cbind( responses, other)
}

ft1 <- cbind(Country=data$SI01, responses[,1:5]) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>%
  align( j=2:6, align="center", part="all" ) %>%
  valign( valign = "top", part="header" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

ft2 <- cbind(Country=data$SI01, responses[,6:ncol(responses)]) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( align="center", part="all" ) %>%
  align( j=1, align="left", part="all") %>%
  align( align="center", part="all" ) %>%
  valign( valign = "top", part="header" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()
  
ft_width <- max( c( flextable_dim(ft1)$widths, 
                    flextable_dim(ft2)$widths ))

ft1 <- ft1 %>% width( width=ft_width)
ft2 <- ft2 %>% width( width=ft_width)
  
ft1 
```

<br>

```{r eval = !amro}
ft2 
```

```{r eval = amro}
disclaimer <- "#### These questions were not included in the dataset shared with AMRO for completion. Please see the Arbovirus Survey Overview for more information."
```

<br>

`r if(amro){ disclaimer }`

