
### Written arbovirus surveillance plans

#### Surveillance plans and the viruses covered (ref Q6, 6b)

```{r}
responses <- get_responses("6")

q6 <- cbind(Country = data$SI01, responses) %>% 
  mutate( Response = recode_factor(.x = Response,
                                   "Yes, we have arbovirus-specific plans(s) or guidelines(s)"="Arbovirus-specific",
                                   "Yes. We do not have arbovirus-specific guidelines, but arboviruses are included within general surveillance guidelines."="Within general surveillance guidelines",
                                   "No"="None",
                                   "I don't know"="Don't know")) %>%
  rename( "Nature of surveillance plans"=Response)

other <- get_responses("6b") %>%
  select(Other)
other <- cbind(Country = data$SI01, other) %>% 
  drop_na(Other) %>%
  rename("Other arbovirus(es) covered" = Other) 

q6b <- get_responses("6b")%>%
  select(-Other)
q6b <- cbind(Country = data$SI01, q6b) %>% 
  pivot_longer(!Country, names_to="Arbovirus", values_to="Response") %>% 
  mutate( Arbovirus = recode_factor(.x = Arbovirus,
                                    "Chikungunya"="CHIKV",
                                    "Dengue"="DENV",
                                    "Yellow fever"="YFV",
                                    "Zika"="ZIKV")) %>% 
  mutate( Response = na_if( Response, "Not selected")) %>% 
  mutate( Response = recode_factor(.x = Response, 
                                   "Yes"="X")) %>% 
  pivot_wider( names_from=Arbovirus, values_from=Response) 

left_join( q6, q6b, by="Country") %>%
  left_join( other) %>%
  regulartable() %>% 
  add_header( CHIKV = "Aedes-borne viruses covered in plans",
              DENV = "Aedes-borne viruses covered in plans",
              YFV = "Aedes-borne viruses covered in plans",
              ZIKV = "Aedes-borne viruses covered in plans" ) %>%
  merge_h( part = "header" ) %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()
```

<br>

#### National programme for arboviral diseases surveillance

```{r}
responses <- get_responses("7")

responses <- cbind(Country = data$SI01, responses) 
specific_programme <- paste( responses$Country[ which( responses$Response == "Specific programme" )], collapse=", ")
another_programme <- paste( responses$Country[ which( responses$Response == "Integrated in another programme" )], collapse=", ")
no_programme <- paste( responses$Country[ which( responses$Response == "No programme" )], collapse=", ")

```

`r specific_programme` reported having a specific arbovirus programme, whereas `r another_programme` 
had arboviral disease surveillance integrated into another programme. No programme reported by `r no_programme`.

<br>

#### Training provided to arboviral surveillance staff (ref Q10)

```{r}
responses <- get_responses("10") %>%
  select(-Other)
# training <- colnames( responses )
colnames(responses) <- c("Basic","Repeat_basic","Advanced","Repeat_advanced","None")
df <- cbind(Country = data$SI01, responses) %>%
  mutate(
    Basic = if_else(Basic == "Yes", "X", " "),
    Repeat_basic = if_else(Repeat_basic == "Yes", "X", " "),
    Advanced = if_else(Advanced == "Yes", "X", " "),
    Repeat_advanced = if_else(Repeat_advanced == "Yes", "X", " "),
    None = if_else(None == "Yes", "X", " ")
  ) %>%
  rename(
    "One-time basic training" = Basic,
    "Repeated/continuing basic training" = Repeat_basic,
    "One-time advanced training" = Advanced,
    "Repeated/continuing advanced training" = Repeat_advanced
  )
# colnames(df) <- c("Country", training)

regulartable(df) %>%
  align(j = 2:6, align = "center") %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()

```

<p>

* _Basic training_:  data capture and analysis (MS Excel, MS Access, EpiInfo) and/or geographic information systems (GIS)
* _Advanced training_: statistical software for data analysis (e.g.  STATA, R, SAS, Tableau, etc)) and GIS

<br>
