---
title: "WHO Global Arbovirus Survey"
author: "Data integrity report"
date: "4 August 2021"
output: 
  ioslides_presentation:
    widescreen: true
    transition: 0
---
<style type="text/css">
slides > slide:not(.nobackground):after {
  content: '';
}
</style>

```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
               # fig.width = 9.64,
               # fig.height = 5.9,
               # fig.path = 'figures/')
options(scipen = '999')
```

```{r}

library(tidyverse)
library(stringr)
library(pander)
library(RColorBrewer)
make_colors <- function(n, seed = 123){
  pal <- RColorBrewer::brewer.pal(n = 9, name = 'Set1')
  set.seed(seed)
  pal <- sample(pal, length(pal))
  out <- colorRampPalette(pal)(n)
  return(out)
}
ggplot2::theme_set(theme_bw())

# get the survey results, as processed by WHO script (lightly edited) :

if( file.exists("data/data.RData" )){
  load("data/data.RData")
} else{
  setwd("misc/")
  source("survey_375147_R_syntax_file.R")
  setwd("../data")
  save(data, file="data.RData")
  setwd("../")
}

# whoa this prints a lot of stuff...
# summary(data)

# load data dictionary to facilitate processing survey results:
dict <- read_csv("misc/Data_dictionary_Survey375147.csv")

# utility function 
get_responses <- function( question_number ){
  idx <- which( dict$`Question number` == question_number )
  # question <- dict$Description[ idx[1] ]
  # cat( paste("Question", question_number, ":", question) )
  var_names <- dict$`Variable name`[idx]
  responses <- data %>% select( all_of(var_names) )
  if( !is.na(dict$Subquestion[ idx[1] ]) ){
    # remove square brackets at beginning and end, then rename:
    colnames( responses ) <- str_extract( dict$Subquestion[idx], '(?<=\\[)[^{}]+(?=\\])')
    # replace square brackets with spaces, then trim whitespace:
    # colnames( responses ) <- trimws( gsub("\\[|\\]", " ",dict$Subquestion[idx]), which="both")
  }
  return( responses )
}

```

## Number of submissions

`r nrow(data)` submissions; `r length(unique(data$SI01))` countries. 

<!-- Multiple submissions from -->
<!-- ```{r echo=FALSE, message=FALSE} -->
<!-- idx <- which( duplicated( data$SI01 ) ) -->
<!-- pander( as.vector(unique( data$SI01[idx] ) ) ) -->
<!-- ``` -->

```{r}
pd <- data %>%
  group_by(Country = SI01) %>%
  tally %>%
  arrange(desc(n)) %>%
  filter(n >= 2) %>%
  bind_rows(
    tibble(Country = 'Others',
           n = 1)
  )
pd$Country <- factor(pd$Country,
                     levels = pd$Country)

ggplot(data = pd,
       aes(x = Country,
           y = n)) +
  geom_bar(stat = 'identity') +
  geom_text(aes(label = n),
            nudge_y = -0.2,
            color = 'white',
            size = 7) +
  labs(y = 'Entries',
       title = 'Survey entries per country')
```

# Surveillance capacity indicators

## Reportable arboviral diseases

**Question 11** :  Is reporting mandatory for any arboviral disease cases in your country? 

```{r}

# relevant questions: q11, q11b

responses <- get_responses("11")
pander( table( responses, useNA="ifany" ))

```

<br>
<br>

**Question 11b** : For which of the following arboviral disease cases is reporting mandatory in your country? (Next 2 slides)

## Reportable arboviral diseases

```{r}

responses <- get_responses("11b")
# summary( responses )
df <- responses %>% 
  pivot_longer(cols=colnames(responses), names_to="Arbovirus", values_to="Response")
knitr::kable( table( df$Arbovirus, df$Response, useNA="ifany") )

```

## Reportable arboviral diseases

```{r}

df <- df %>% 
  group_by(Arbovirus, Response) %>% 
  tally
ggplot(df, aes(x=Response, y=n, fill=Response)) + 
  geom_col() + 
  facet_wrap(~Arbovirus) +
  theme(legend.position = "bottom",
        legend.direction="horizontal",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  guides(fill=guide_legend(ncol=2)) +
  scale_fill_manual(name = '',
                    values = make_colors(length(unique(df$Response)))) +
  labs(y = 'Responses')

```

##  History of arbovirus circulation since 2000 

**Question 5** :  Which arboviruses have circulated in your country at any time since the year 2000?  This refers only to arboviruses with autochthonous i.e., local mosquito-borne transmission

```{r}

# relevant question: q5

responses <- get_responses("5")
other <- responses %>% select(Other)
responses <- responses %>% select(-Other)
df <- responses %>% 
  pivot_longer(cols=colnames(responses), names_to="Arbovirus", values_to="Response")
pander( table( df$Arbovirus, df$Response, useNA="ifany") )

# knitr::kable( table(other))
```

##  History of arbovirus circulation since 2000 

```{r}

ggplot(data = df %>% filter(Response == 'Yes'),
       aes(x = Arbovirus)) +
  geom_bar() +
  labs(y = 'Entries')

```

##  Conducting surveillance 

**Question 12** :  In the last 2 years, did your country conduct national epidemiological surveillance for human cases of arboviral disease? 

```{r}

# relevant question: q12 (surveillance on humans)

responses <- get_responses("12")
pander( table(responses, useNA="ifany"))

```

##  Conducting surveillance 

**Question 28** : For the last 2 years, did your country conduct entomologic surveillance for arboviral infections in mosquito vectors?

```{r}
# relevant question: q28 (surveillance on vectors)

responses <- get_responses("28")
pander( table(responses, useNA="ifany"))

```

##  Conducting surveillance 

**Question 41** : During the last 2 years, did your country conduct national epidemiological surveillance for arboviral disease in animals (eg, epizootic surveillance for yellow fever in endemic areas)?

```{r}

# relevant question: q41 (surveillance on animals)

responses <- get_responses("41")
pander( table(responses, useNA="ifany"))

```

## Training of surveillance personnel and clinicians

**Question 10** : Which training has been provided to the staff working on arboviral disease surveillance data

```{r}

# relevant question: q10 

responses <- get_responses("10")
other <- responses %>% select(Other)
responses <- responses %>% select(-Other)
df <- responses %>% 
  pivot_longer(cols=colnames(responses), names_to="Arbovirus", values_to="Response")
knitr::kable( table( df$Arbovirus, df$Response, useNA="ifany") )

```

## Training of surveillance personnel and clinicians

**Question 24** : Does your country provide regular training sessions for healthcare workers on clinical diagnosis and management of Aedes-borne arboviral diseases?

```{r}
# relevant question: q24

responses <- get_responses("24")
colnames(responses) <- c("Selection", "Comments")
knitr::kable( table(responses$Selection, useNA="ifany"))
# knitr::kable( table(responses$Comments, useNA="ifany"))

```

# Laboratory diagnostic capacity indicators

## Testing in outbreak vs non-outbreak settings

**Question 15** : Is arbovirus diagnostic laboratory testing performed for confirmation of suspected cases in your country? (Please select the applicable option during outbreak periods and  during non-outbreak periods, respectively)   

```{r}

# relevant question: q15

responses <- get_responses("15")
df <- responses %>%
  pivot_longer(cols=colnames(responses), names_to="Arbovirus", values_to="Response")
knitr::kable( table( df$Arbovirus, df$Response, useNA="ifany") )

```

## Laboratory tests available

**Question 17** :  Overall, what arboviral testing capacity(ies) is(are) available in your country? Please check all applicable boxes

```{r}

# relevant question: q17

responses <- get_responses("17")
df <- responses %>%
  pivot_longer(cols=colnames(responses), names_to="Testing", values_to="Response")
new_cols <- matrix( unlist( strsplit(df$Testing, "\\]\\[") ), ncol=2, byrow=T)
df <- df %>% 
  mutate(Arbovirus = new_cols[,1], Testing = new_cols[,2])
df$Response <- as.numeric( df$Response)
df <- df %>% 
  group_by(Arbovirus, Testing) %>% 
  summarize(Total = sum(Response, na.rm=T))
df$Arbovirus <- factor( df$Arbovirus )
df$Testing <- factor( df$Testing )
mat <- matrix( data=df$Total, ncol=length(levels(df$Arbovirus)), byrow=F)
colnames( mat ) <- levels( df$Arbovirus )
rownames( mat ) <- levels( df$Testing )
knitr::kable( mat )

ggplot(df, aes(x=Testing, y=Total, fill=Testing)) + 
  geom_col() + 
  facet_wrap(~Arbovirus) + 
  theme(legend.position = "bottom",
        legend.direction="horizontal",
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  scale_fill_manual(name = '',
                    values = make_colors(length(unique(df$Testing))))

```

# Response capacity indicators

## Surveillance and control plans available

**Question 6** : Do you have any written arbovirus surveillance and control plan(s) and/or guideline(s) for your country?

```{r}

# relevant question: q6

responses <- get_responses("6")
knitr::kable( table(responses, useNA="ifany"))

```

## Vector control method employed

**Question 35** : Over the past two years, did your country use any of the following vector control methods in local jurisdictions (either using government staff and resources, or subcontracting to a different entity to do so)? Please select all that apply

```{r}

# relevant question: q35

responses <- get_responses("35")
other <- responses %>% select(Other)
df <- responses %>% 
  select(-Other) %>%
  pivot_longer(cols=colnames(responses)[1:5], names_to="Method", values_to="Response")

knitr::kable( table(df$Method, df$Response, useNA="ifany"))

```

##   Surveillance and response committee exists

**Question 47** : Is there either a surveillance and outbreak response committee in your country, or a steering committee for that purpose?

```{r}

# relevant question: q47

responses <- get_responses("47")
pander( table(responses, useNA="ifany"))

```

##  Contingency plan exists

**Question 48** : Does your country have a contingency plan to organize healthcare services during an outbreak (including outbreaks of arboviral diseases)?

```{r}

# relevant question: q48

responses <- get_responses("48")
pander( table(responses, useNA="ifany"))

```

# Epidemiologic risk data

## Vectors present and level of risk

**Question 34** :  Is there a record of Aedes aegypti or Aedes albopictus being found in your country in the past 5 years? Please choose only one of the following

```{r}

# relevant question: q34

responses <- get_responses("34")
knitr::kable( table(responses, useNA="ifany"))

```

## Vectors present and level of risk

**Question 34b** :  Please describe the potential public health threat from Aedes aegypti in your country

```{r}

# relevant question: q34b

responses <- get_responses("34b")
colnames(responses) <- c("Selection", "Other")
knitr::kable( table(responses$Selection, useNA="ifany"))

```

## Vectors present and level of risk

**Question 34b** :  Please describe the potential public health threat from Aedes aegypti in your country

```{r}
knitr::kable( table(responses$Other, useNA="ifany"))

```

## Vectors present and level of risk

**Question 34c** :  Please describe the potential public health threat from Aedes albopictus in your country

```{r}

# relevant question: q34c

responses <- get_responses("34c")
colnames(responses) <- c("Selection", "Other")
knitr::kable( table(responses$Selection, useNA="ifany"))

```

## Vectors present and level of risk

**Question 34c** :  Please describe the potential public health threat from Aedes albopictus in your country

```{r}
knitr::kable( table(responses$Other, useNA="ifany"))

```

## All arboviruses 2015-2020 (cases and deaths) 

**Question 55b** : Were cases of other mosquito-borne arboviruses, not listed in the previous question, reported in your country from 2015-2020?

```{r}

# relevant question: q55b

responses <- get_responses("55b")
pander( table(responses, useNA="ifany"))

```

## All arboviruses 2015-2020 (cases and deaths) 

**Question 55c** : Please select any of the following other mosquito-borne viruses that have been reported in your country from 2015-2020

```{r}

# relevant question: q55c

responses <- get_responses("55c")
df <- responses %>%
  pivot_longer(cols=colnames(responses), names_to="Arbovirus", values_to="Response") %>%
  filter(Response=="Yes") %>%
  droplevels()
pander( table( df$Arbovirus, df$Response, useNA="ifany") )

```
