---
title: " "
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
ggplot2::theme_set(ggplot2::theme_bw())

# options(scipen = '999')
```

```{js}
element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true){
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }


});

```

```{css, echo=FALSE}
h4 {
  text-align: center;
}
```

```{r, echo = FALSE}
source('../functions.R')
dict <- load_dict()
data <- load_data()
```


```{r}
data <- data %>% filter(Region=='SEARO') %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

caption <- "Frequency and scope of entomologic surveillance (ref Q28c, 28d, 28e)"
q28e <- get_responses("28e")
colnames( q28e ) <- c("How_often", "Other")
q28e <- q28e %>%
  mutate( How_often = factor( replace_na( as.character(How_often), ""))) %>%
  mutate( Other = factor( replace_na( as.character(Other), ""))) %>%
  unite( Response, How_often:Other, sep="") 
q28e <- cbind( Country = data$SI01, q28e)

q28c <- get_responses("28c")
colnames( q28c ) <- c("Scope", "Comments")
q28c <- q28c %>%
  mutate( Scope = recode_factor(.x = Scope,
                                   "Country wide"="Country wide",
                                   "Restricted to specific locations . Please specify where:"="Restricted to specific locations",
                                   "Don’t know"="I don’t know"))
responses <- cbind( q28e, q28c)

q28d <- get_responses("28d")
q28d <- cbind( Country = data$SI01, q28d) %>% 
  drop_na(Response) %>%
  mutate( Response = paste0("(", Response, " sentinel sites)")) %>%
  rename( "Sites" = Response )

left_join( responses, q28d, by="Country") %>%
  mutate( Scope = as.character( Scope ) ) %>%
  replace_na( list( Scope = "", Sites = "")) %>%
  unite( "Geographic scope", c("Scope", "Sites"), sep = "\n") %>%
  regulartable( ) %>% 
  set_caption(caption) %>% autofit()

