---
title: ' '
pagetitle: 'AMRO Q11'
output:
  html_document:
    includes:
      in_header: AMRO_Q11_header.html
params:
  region: AMRO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{js}
// Region dropdown
/* When the user clicks on the button,
toggle between hiding and showing the dropdown content */
function myFunction() {
  document.getElementById("myDropdown").classList.toggle("show");
}

// Close the dropdown menu if the user clicks outside of it
window.onclick = function(event) {
  if (!event.target.matches('.dropbtn')) {
    var dropdowns = document.getElementsByClassName("dropdown-content");
    var i;
    for (i = 0; i < dropdowns.length; i++) {
      var openDropdown = dropdowns[i];
      if (openDropdown.classList.contains('show')) {
        openDropdown.classList.remove('show');
      }
    }
  }
}
// end region dropdown

element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Overview of data  */
    var overview_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        overview_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }
    
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true) {
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    /* #regional-navigation-disease-surveillance  */
    var regional_menu_opened = $('#regional-navigation-disease-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-disease-surveillance').length &&
        !$(e.target).is('#regional-navigation-disease-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-disease-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-lab-capacity  */
    var regional_menu_opened = $('#regional-navigation-lab-capacity').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-lab-capacity').length &&
        !$(e.target).is('#regional-navigation-lab-capacity') &&
        regional_menu_opened === true) {
            $('#regional-navigation-lab-capacity').collapse('toggle');
    }
    
    /* #regional-navigation-management  */
    var regional_menu_opened = $('#regional-navigation-management').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-management').length &&
        !$(e.target).is('#regional-navigation-management') &&
        regional_menu_opened === true) {
            $('#regional-navigation-management').collapse('toggle');
    }
    
    /* #regional-navigation-vector-surveillance  */
    var regional_menu_opened = $('#regional-navigation-vector-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-vector-surveillance').length &&
        !$(e.target).is('#regional-navigation-vector-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-vector-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-community  */
    var regional_menu_opened = $('#regional-navigation-community').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-community').length &&
        !$(e.target).is('#regional-navigation-community') &&
        regional_menu_opened === true) {
            $('#regional-navigation-community').collapse('toggle');
    }
    
    /* #regional-navigation-preparedness  */
    var regional_menu_opened = $('#regional-navigation-preparedness').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-preparedness').length &&
        !$(e.target).is('#regional-navigation-preparedness') &&
        regional_menu_opened === true) {
            $('#regional-navigation-preparedness').collapse('toggle');
    }
    
    /* #regional-navigation-surveillance-staffing  */
    var regional_menu_opened = $('#regional-navigation-surveillance-staffing').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-surveillance-staffing').length &&
        !$(e.target).is('#regional-navigation-surveillance-staffing') &&
        regional_menu_opened === true) {
            $('#regional-navigation-surveillance-staffing').collapse('toggle');
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }

});

```

```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
region_countries <- load_regions_countries()
```

```{r}
data <- data %>% filter(Region==params$region) %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

#### Reportable diseases by case classification status (ref Q11b, 11c)

```{r}
q11b <- get_responses("11b")
q11b <- cbind(Country = data$SI01, q11b) %>%
  select(-"Other ") %>% 
  pivot_longer(!Country, names_to = "Arbovirus", values_to = "Response")
q11b$Response <- str_to_sentence(gsub("Mandatory reporting of ", "", q11b$Response))
q11b <- q11b %>%
  mutate( Arbovirus = recode_factor(.x = Arbovirus,
                                    "Chikungunya" = "CHIKV",
                                    "Dengue" = "DENV",
                                    "Yellow fever" = "YFV",
                                    "Zika (congenital)" = "ZIKV (C)",
                                    "Zika (non-congenital)" = "ZIKV (NC)")) %>%
  mutate( Response = recode_factor( .x = Response,
                                    "All suspect cases" = "S",
                                    "Confirmed cases only" = "C",
                                    "Not reportable" = "N")) %>%
  pivot_wider(names_from = Arbovirus, values_from = Response) 

q11c <- get_responses("11c")
idx <- which( grepl("Arbovirus",colnames(q11c)))
arboviruses <- cbind( Country=data$SI01, q11c[,idx]) %>%
  pivot_longer(!Country) %>%
  select( Country, Arbovirus=value)
reporting <- cbind( Country=data$SI01, q11c[,-idx]) %>%
  pivot_longer(!Country) %>%
  select( Country, Reporting=value)
idx <- grep("suspect", str_to_lower(reporting$Reporting))
reporting$Reporting[idx] <- " (S)"
idx <- grep("confirm", str_to_lower(reporting$Reporting))
reporting$Reporting[idx] <- " (C)"
idx <- grep("not", str_to_lower(reporting$Reporting))
reporting$Reporting[idx] <- " (N)"
reporting$Reporting[ is.na( reporting$Reporting) ] <- ""
q11c <- cbind(arboviruses, Reporting = reporting$Reporting) %>%
  unite( "Other", Arbovirus:Reporting, sep = "")
idx <- which( q11c$Other == "NA" )
q11c <- q11c[-idx,]
q11c <- q11c %>% 
  group_by( Country ) %>% 
  summarize( Other = paste(Other, collapse=", "))

left_join( q11b, q11c) %>%
  regulartable() %>%
  merge_v(j = ~Country ) %>%
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  footnote( j=2:6,
            part="header",
            value = as_paragraph("S = All suspect cases; C = Confirmed cases only; N = Not reportable"),
            ref_symbols = "a") %>%
  footnote( j=7,
            part="header",
            value = as_paragraph("CCHFV = Crimean Congo haemorrhagic fever virus; CHIKV = chikungunya virus; DENV = dengue virus; EEEV = Eastern equine encephalitis virus; MAYV = Mayaro virus; OROV = Oropouche virus; RVFV = Rift Valley fever virus; SFFV = Sand fly fever virus (Naples, Sicilian); TBEV = Tick-borne encephalitis virus; TOSV = Toscana virus; VEEV = Venezuelan equine encephalitis virus; WNV = West Nile virus; YFV = yellow fever virus"),
            ref_symbols = "b", inline = FALSE) %>%
  color( color="#FFFFFF", part="header" ) %>% 
  align( j=2:6, align="center", part="all" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

```

<br>

### Surveillance for human cases of arboviral disease

#### Performance of national epidemiological surveillance for arboviral diseases in humans (ref Q12, 12b, 12c)

```{r}
responses_12 <- get_responses("12") 
responses_12b <- get_responses("12b")
colnames( responses_12b ) <- c("Response", "Other")
responses_12b <- responses_12b %>%
  mutate( Response = factor( replace_na( as.character(Response), ""))) %>%
  mutate( Other = factor( replace_na( as.character(Other), ""))) %>%
  unite( Frequency, Response:Other, sep="") 

responses_12c <- get_responses("12c")
colnames(responses_12c) <- "Type"

cbind(Country = data$SI01, responses_12, responses_12b, responses_12c) %>% 
  rename( "Surveillance conducted" = Response ) %>% 
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

```

<br>

### Training sessions for healthcare workers on notification of _Aedes_-borne arboviral diseases

#### Training of healthcare workers on reporting _Aedes_-borne arboviral diseases (ref Q13)

```{r}
responses <- get_responses("13") 
colnames(responses) <- c("Response","Description")
responses <- responses %>%
  mutate(Response = recode_factor(.x=Response,
                                  "Yes. If so, please describe in the comments field:"="Yes",
                                  "No"="No",
                                  "I don't know" ="I don't know")) 
cbind(Country = data$SI01, responses) %>% 
  filter( Response == "Yes") %>% 
  select(-Response) %>%
  replace_na( list(Description = "Conducted (no further description provided)")) %>% 
  rename( "Description of training" = Description) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

```
