---
title: ' '
pagetitle: 'AMRO Q29 global'
output:
  html_document:
    includes:
      in_header: AMRO_Q29_global_header.html
params:
  region: AMRO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{js}
// Region dropdown
/* When the user clicks on the button,
toggle between hiding and showing the dropdown content */
function myFunction() {
  document.getElementById("myDropdown").classList.toggle("show");
}

// Close the dropdown menu if the user clicks outside of it
window.onclick = function(event) {
  if (!event.target.matches('.dropbtn')) {
    var dropdowns = document.getElementsByClassName("dropdown-content");
    var i;
    for (i = 0; i < dropdowns.length; i++) {
      var openDropdown = dropdowns[i];
      if (openDropdown.classList.contains('show')) {
        openDropdown.classList.remove('show');
      }
    }
  }
}
// end region dropdown

element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Overview of data  */
    var overview_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        overview_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }
    
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true) {
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    /* #regional-navigation-disease-surveillance  */
    var regional_menu_opened = $('#regional-navigation-disease-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-disease-surveillance').length &&
        !$(e.target).is('#regional-navigation-disease-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-disease-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-lab-capacity  */
    var regional_menu_opened = $('#regional-navigation-lab-capacity').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-lab-capacity').length &&
        !$(e.target).is('#regional-navigation-lab-capacity') &&
        regional_menu_opened === true) {
            $('#regional-navigation-lab-capacity').collapse('toggle');
    }
    
    /* #regional-navigation-management  */
    var regional_menu_opened = $('#regional-navigation-management').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-management').length &&
        !$(e.target).is('#regional-navigation-management') &&
        regional_menu_opened === true) {
            $('#regional-navigation-management').collapse('toggle');
    }
    
    /* #regional-navigation-vector-surveillance  */
    var regional_menu_opened = $('#regional-navigation-vector-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-vector-surveillance').length &&
        !$(e.target).is('#regional-navigation-vector-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-vector-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-community  */
    var regional_menu_opened = $('#regional-navigation-community').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-community').length &&
        !$(e.target).is('#regional-navigation-community') &&
        regional_menu_opened === true) {
            $('#regional-navigation-community').collapse('toggle');
    }
    
    /* #regional-navigation-preparedness  */
    var regional_menu_opened = $('#regional-navigation-preparedness').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-preparedness').length &&
        !$(e.target).is('#regional-navigation-preparedness') &&
        regional_menu_opened === true) {
            $('#regional-navigation-preparedness').collapse('toggle');
    }
    
    /* #regional-navigation-surveillance-staffing  */
    var regional_menu_opened = $('#regional-navigation-surveillance-staffing').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-surveillance-staffing').length &&
        !$(e.target).is('#regional-navigation-surveillance-staffing') &&
        regional_menu_opened === true) {
            $('#regional-navigation-surveillance-staffing').collapse('toggle');
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }

});

```

```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
region_countries <- load_regions_countries()
```

```{r}
data <- data %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

### Vector surveillance and control

#### Countries conducting mosquito surveillance, by stage and species identification (ref Q29, 30, 31)

```{r}
q29 <- get_responses("29")
q29 <- cbind( Region = data$Region, q29 )
nums <- q29 %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
q29 <- q29 %>% 
  filter( Response == "Yes" ) %>% 
  group_by( Region)  %>%
  tally() %>%
  right_join( nums, by="Region") %>%
  replace_na( list(n = 0)) %>%
  mutate( Percentage = paste0( "(", round( 100*n/n_countries), "%)" )) %>%
  select(Region, n, Percentage) %>%
  unite( "Adult surveillance", n:Percentage, sep=" " )

q30 <- get_responses("30")
q30 <- cbind( Region = data$Region, q30 )
nums <- q30 %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
q30 <- q30 %>% 
  filter( Response == "Yes" ) %>% 
  group_by( Region)  %>%
  tally() %>%
  right_join( nums, by="Region") %>%
  replace_na( list(n = 0)) %>%
  mutate( Percentage = paste0( "(", round( 100*n/n_countries), "%)" )) %>%
  select(Region, n, Percentage) %>%
  unite( "Larval/pupal surveillance", n:Percentage, sep=" " )

q31 <- get_responses("31")
q31 <- cbind( Region = data$Region, q31 )
nums <- q31 %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
q31 <- q31 %>% 
  filter( Response == "Yes" ) %>% 
  group_by( Region)  %>%
  tally() %>%
  right_join( nums, by="Region") %>%
  replace_na( list(n = 0)) %>%
  mutate( Percentage = paste0( "(", round( 100*n/n_countries), "%)" )) %>%
  select(Region, n, Percentage) %>%
  unite( "Trapped mosquitoes identified to species", n:Percentage, sep=" " )

left_join( q29, q30, by="Region") %>%
  left_join( q31, by="Region") %>%
  rename("Regional office" = Region ) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( j=2:4, align="center", part="all" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

```

<br>

#### Vector control methods used in local jurisdictions in the past two years (either using government staff and resources, or subcontracting to a different entity to do so) (ref Q35)

```{r}
responses <- get_responses("35")
responses <- cbind( Region = data$Region, responses) %>% 
  drop_na(Region) 
nums <- responses %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
other <- responses %>% select(Other)

responses %>% 
  select(-Other) %>% 
  mutate( across(!Region, ~ ifelse(.x == "Yes", 1, 0))) %>%
  group_by(Region) %>%
  summarize( across(everything(), ~ sum(.x, na.rm=TRUE))) %>%
  ungroup() %>%
  left_join( nums, by="Region") %>%
  group_by(Region) %>%
  mutate( across( everything(), ~ paste0( .x, " (", round(100*(.x)/n_countries), "%)") ) ) %>%
  select(-n_countries) %>%
  rename("Regional office" = Region,
         "Adulticiding"="Adulticiding (insecticide application against adult mosquitoes)",
         "Insect growth regulators" = "Insect growth regulators (eg , pyriproxyfen)") %>%
  regulartable %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( j=2:7, align="center", part="all" ) %>%
  compose( j=5, part="header", value = as_paragraph(as_i("Wolbachia"), " method")) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit() 

```

<br>

#### Vector indices measured and calculation of infection rates (ref Q37b)

```{r}
responses <- get_responses("37b")
responses <- cbind( Region = data$Region, responses) %>% 
  drop_na(Region) 
nums <- responses %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
other <- responses %>% select(Other)
responses %>% 
  select(-Other) %>% 
  mutate( across(!Region, ~ ifelse(.x == "Yes", 1, 0))) %>%
  group_by(Region) %>%
  summarize( across(everything(), ~ sum(.x, na.rm=TRUE))) %>%
  ungroup() %>%
  left_join( nums, by="Region") %>%
  group_by(Region) %>%
  mutate( across( everything(), ~ paste0( .x, " (", round(100*(.x)/n_countries), "%)") ) ) %>%
  select(-n_countries) %>%
  rename("Regional office" = Region ) %>%
  regulartable %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( j=2:7, align="center", part="all" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit() 
```
