---
title: "Country data"
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
# options(scipen = '999')
```

```{r, child="_sessioninfo.Rmd"}
```

```{r, echo = FALSE}
source('functions.R')
df <- load_data()
```


# Surveillance capacity indicators

### Reportable arboviral diseases

(q11, q11b)

### History of any arbovirus circulation since 2000 

(q5)


### Conducting surveillance on humans

(q12)

### Conducting surveillance on vectors 

(q28) 


### Conducting surveillance on animals 

(q41)

### Training of surveillance personnel and clinicians

(q10) (q24)

### Presence written arbovirus surveillance and control plans

(q6)

### Arbovirus program independent or integrated

(q7)

### Tools for case reporting 

(q9)

# Laboratory diagnostic indicators


### Testing in outbreak vs non-outbreak settings 

(q15)

### Laboratory tests available 

(q17)

### Serotyping and sequencing capacity? 

(q19)


# Response capacity indicators

### Surveillance and control plans available 

(q 6)

### Clinical guidelines for healthcare workers 

(q21)


### Vector control method employed (q35)


### Surveillance and response committee exists (q47)


### Contingency plan exists (q48)


### Most common vector control methods used 

(q35)


### Indicators used for thresholds 

(q37, 37b, 38)


### Insecticide resistance

(q39)

### Criteria for declaring an outbreak

(q49)


# Epidemiological risk data


### Vectors present and level of risk 

(q34, q34b, q34c)

### Entomological surveillance in the last 2 years

(q28)


### How often is conducted

(q28e)


### Vectors recorded in the last 5 years  and the public health threat 

(q34)
(34b, 34c)


### All arboviruses 2015-2020 (cases and deaths) 

(q55, b, c)


### Most recent year data 

(q56)

