---
title: ' '
pagetitle: 'EURO Q6'
output:
  html_document:
    includes:
      in_header: EURO_Q6_header.html
params:
  region: EURO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{js}
// Region dropdown
/* When the user clicks on the button,
toggle between hiding and showing the dropdown content */
function myFunction() {
  document.getElementById("myDropdown").classList.toggle("show");
}

// Close the dropdown menu if the user clicks outside of it
window.onclick = function(event) {
  if (!event.target.matches('.dropbtn')) {
    var dropdowns = document.getElementsByClassName("dropdown-content");
    var i;
    for (i = 0; i < dropdowns.length; i++) {
      var openDropdown = dropdowns[i];
      if (openDropdown.classList.contains('show')) {
        openDropdown.classList.remove('show');
      }
    }
  }
}
// end region dropdown

element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Overview of data  */
    var overview_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        overview_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }
    
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true) {
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    /* #regional-navigation-disease-surveillance  */
    var regional_menu_opened = $('#regional-navigation-disease-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-disease-surveillance').length &&
        !$(e.target).is('#regional-navigation-disease-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-disease-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-lab-capacity  */
    var regional_menu_opened = $('#regional-navigation-lab-capacity').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-lab-capacity').length &&
        !$(e.target).is('#regional-navigation-lab-capacity') &&
        regional_menu_opened === true) {
            $('#regional-navigation-lab-capacity').collapse('toggle');
    }
    
    /* #regional-navigation-management  */
    var regional_menu_opened = $('#regional-navigation-management').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-management').length &&
        !$(e.target).is('#regional-navigation-management') &&
        regional_menu_opened === true) {
            $('#regional-navigation-management').collapse('toggle');
    }
    
    /* #regional-navigation-vector-surveillance  */
    var regional_menu_opened = $('#regional-navigation-vector-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-vector-surveillance').length &&
        !$(e.target).is('#regional-navigation-vector-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-vector-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-community  */
    var regional_menu_opened = $('#regional-navigation-community').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-community').length &&
        !$(e.target).is('#regional-navigation-community') &&
        regional_menu_opened === true) {
            $('#regional-navigation-community').collapse('toggle');
    }
    
    /* #regional-navigation-preparedness  */
    var regional_menu_opened = $('#regional-navigation-preparedness').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-preparedness').length &&
        !$(e.target).is('#regional-navigation-preparedness') &&
        regional_menu_opened === true) {
            $('#regional-navigation-preparedness').collapse('toggle');
    }
    
    /* #regional-navigation-surveillance-staffing  */
    var regional_menu_opened = $('#regional-navigation-surveillance-staffing').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-surveillance-staffing').length &&
        !$(e.target).is('#regional-navigation-surveillance-staffing') &&
        regional_menu_opened === true) {
            $('#regional-navigation-surveillance-staffing').collapse('toggle');
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }

});

```

```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
region_countries <- load_regions_countries()
```

```{r}
data <- data %>% filter(Region==params$region) %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

### Written arbovirus surveillance plans

#### Surveillance plans and the viruses covered (ref Q6, 6b)

```{r}
responses <- get_responses("6")

q6 <- cbind(Country = data$SI01, responses) %>% 
  mutate( Response = recode_factor(.x = Response,
                                   "Yes, we have arbovirus-specific plans(s) or guidelines(s)"="Arbovirus-specific",
                                   "Yes. We do not have arbovirus-specific guidelines, but arboviruses are included within general surveillance guidelines."="Within general surveillance guidelines",
                                   "No"="None",
                                   "I don't know"="Don't know")) %>%
  rename( "Nature of surveillance plans"=Response)

other <- get_responses("6b") %>%
  select(Other)
other <- cbind(Country = data$SI01, other) %>% 
  drop_na(Other) %>%
  rename("Other arbovirus(es) covered" = Other) 

q6b <- get_responses("6b")%>%
  select(-Other)
q6b <- cbind(Country = data$SI01, q6b) %>% 
  pivot_longer(!Country, names_to="Arbovirus", values_to="Response") %>% 
  mutate( Arbovirus = recode_factor(.x = Arbovirus,
                                    "Chikungunya"="CHIKV",
                                    "Dengue"="DENV",
                                    "Yellow fever"="YFV",
                                    "Zika"="ZIKV")) %>% 
  mutate( Response = na_if( Response, "Not selected")) %>% 
  mutate( Response = recode_factor(.x = Response, 
                                   "Yes"="X")) %>% 
  pivot_wider( names_from=Arbovirus, values_from=Response) 

left_join( q6, q6b, by="Country") %>%
  left_join( other) %>%
  regulartable() %>% 
  add_header( CHIKV = "Aedes-borne viruses covered in plans",
              DENV = "Aedes-borne viruses covered in plans",
              YFV = "Aedes-borne viruses covered in plans",
              ZIKV = "Aedes-borne viruses covered in plans" ) %>%
  merge_h( part = "header" ) %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()
```

<br>

#### National programme for arboviral diseases surveillance

```{r}
responses <- get_responses("7")

responses <- cbind(Country = data$SI01, responses) 
specific_programme <- paste( responses$Country[ which( responses$Response == "Specific programme" )], collapse=", ")
another_programme <- paste( responses$Country[ which( responses$Response == "Integrated in another programme" )], collapse=", ")
no_programme <- paste( responses$Country[ which( responses$Response == "No programme" )], collapse=", ")

```

`r specific_programme` reported having a specific arbovirus programme, whereas `r another_programme` 
had arboviral disease surveillance integrated into another programme. No programme reported by `r no_programme`.

<br>

#### Training provided to arboviral surveillance staff (ref Q10)

```{r}
responses <- get_responses("10") %>%
  select(-Other)
# training <- colnames( responses )
colnames(responses) <- c("Basic","Repeat_basic","Advanced","Repeat_advanced","None")
df <- cbind(Country = data$SI01, responses) %>%
  mutate(
    Basic = if_else(Basic == "Yes", "X", " "),
    Repeat_basic = if_else(Repeat_basic == "Yes", "X", " "),
    Advanced = if_else(Advanced == "Yes", "X", " "),
    Repeat_advanced = if_else(Repeat_advanced == "Yes", "X", " "),
    None = if_else(None == "Yes", "X", " ")
  ) %>%
  rename(
    "One-time basic training" = Basic,
    "Repeated/continuing basic training" = Repeat_basic,
    "One-time advanced training" = Advanced,
    "Repeated/continuing advanced training" = Repeat_advanced
  )
# colnames(df) <- c("Country", training)

regulartable(df) %>%
  align(j = 2:6, align = "center") %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()

```

<p>

* _Basic training_:  data capture and analysis (MS Excel, MS Access, EpiInfo) and/or geographic information systems (GIS)
* _Advanced training_: statistical software for data analysis (e.g.  STATA, R, SAS, Tableau, etc)) and GIS

<br>
