---
title: ' '
pagetitle: 'EURO Q28'
output:
  html_document:
    includes:
      in_header: EURO_Q28_header.html
params:
  region: EURO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{js}
// Region dropdown
/* When the user clicks on the button,
toggle between hiding and showing the dropdown content */
function myFunction() {
  document.getElementById("myDropdown").classList.toggle("show");
}

// Close the dropdown menu if the user clicks outside of it
window.onclick = function(event) {
  if (!event.target.matches('.dropbtn')) {
    var dropdowns = document.getElementsByClassName("dropdown-content");
    var i;
    for (i = 0; i < dropdowns.length; i++) {
      var openDropdown = dropdowns[i];
      if (openDropdown.classList.contains('show')) {
        openDropdown.classList.remove('show');
      }
    }
  }
}
// end region dropdown

element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Overview of data  */
    var overview_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        overview_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }
    
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true) {
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    /* #regional-navigation-disease-surveillance  */
    var regional_menu_opened = $('#regional-navigation-disease-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-disease-surveillance').length &&
        !$(e.target).is('#regional-navigation-disease-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-disease-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-lab-capacity  */
    var regional_menu_opened = $('#regional-navigation-lab-capacity').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-lab-capacity').length &&
        !$(e.target).is('#regional-navigation-lab-capacity') &&
        regional_menu_opened === true) {
            $('#regional-navigation-lab-capacity').collapse('toggle');
    }
    
    /* #regional-navigation-management  */
    var regional_menu_opened = $('#regional-navigation-management').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-management').length &&
        !$(e.target).is('#regional-navigation-management') &&
        regional_menu_opened === true) {
            $('#regional-navigation-management').collapse('toggle');
    }
    
    /* #regional-navigation-vector-surveillance  */
    var regional_menu_opened = $('#regional-navigation-vector-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-vector-surveillance').length &&
        !$(e.target).is('#regional-navigation-vector-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-vector-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-community  */
    var regional_menu_opened = $('#regional-navigation-community').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-community').length &&
        !$(e.target).is('#regional-navigation-community') &&
        regional_menu_opened === true) {
            $('#regional-navigation-community').collapse('toggle');
    }
    
    /* #regional-navigation-preparedness  */
    var regional_menu_opened = $('#regional-navigation-preparedness').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-preparedness').length &&
        !$(e.target).is('#regional-navigation-preparedness') &&
        regional_menu_opened === true) {
            $('#regional-navigation-preparedness').collapse('toggle');
    }
    
    /* #regional-navigation-surveillance-staffing  */
    var regional_menu_opened = $('#regional-navigation-surveillance-staffing').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-surveillance-staffing').length &&
        !$(e.target).is('#regional-navigation-surveillance-staffing') &&
        regional_menu_opened === true) {
            $('#regional-navigation-surveillance-staffing').collapse('toggle');
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }

});

```

```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
region_countries <- load_regions_countries()
```

```{r}
data <- data %>% filter(Region==params$region) %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

#### Entomologic surveillance conducted for arboviral infections in mosquito vectors in the past two years (ref Q28)

```{r}
responses <- get_responses("28")
responses <- cbind(Country = data$SI01, responses)
conducted <- responses$Country[which(responses$Response == "Yes")]
not_conducted <- responses$Country[which(responses$Response == "No")]
no_response <- responses$Country[which(is.na(responses$Response))]

```

Countries that conducted entomologic surveillance included `r conducted`. Countries that did not included
`r not_conducted`. `r no_response` did not respond. 

<br>
 
#### Frequency and scope of entomologic surveillance (ref Q28c, 28d, 28e)

```{r}
q28e <- get_responses("28e")
colnames( q28e ) <- c("How_often", "Other")
q28e <- q28e %>%
  mutate( How_often = factor( replace_na( as.character(How_often), ""))) %>%
  mutate( Other = factor( replace_na( as.character(Other), ""))) %>%
  unite( Response, How_often:Other, sep="") 
q28e <- cbind( Country = data$SI01, q28e)

q28c <- get_responses("28c")
colnames( q28c ) <- c("Scope", "Comments")
q28c <- q28c %>%
  mutate( Scope = recode_factor(.x = Scope,
                                   "Country wide"="Country wide",
                                   "Restricted to specific locations . Please specify where:"="Restricted to specific locations",
                                   "Don’t know"="I don’t know"))
responses <- cbind( q28e, q28c)

q28d <- get_responses("28d")
q28d <- cbind( Country = data$SI01, q28d) %>% 
  drop_na(Response) %>%
  mutate( Response = paste0("(", Response, " sentinel sites)")) %>%
  rename( "Sites" = Response )

left_join( responses, q28d, by="Country") %>%
  mutate( Scope = as.character( Scope ) ) %>%
  replace_na( list( Scope = "", Sites = "")) %>%
  unite( "Geographic scope", c("Scope", "Sites"), sep = "\n") %>%
  regulartable( ) %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()
```

<br>

### Performance of adult and larval/pupal mosquito surveillance

<br>

#### Mosquito surveillance and identification (ref Q29, 30, 31)

```{r}
q29 <- get_responses("29")
q29 <- q29 %>% 
  mutate( Response = recode_factor(.x=Response,
                                   "Yes"="X",
                                   "No"=" ")) %>%
  rename("Adult surveillance"="Response") 
q30 <- get_responses("30")
q30 <- q30 %>% 
  mutate( Response = recode_factor(.x=Response,
                                   "Yes"="X",
                                   "No"=" ")) %>%
  rename("Larval/pupal surveillance"="Response")
q31 <- get_responses("31")
q31 <- q31 %>% 
  mutate( Response = recode_factor(.x=Response,
                                   "Yes"="X",
                                   "No"=" ")) %>%
  rename("Trapped mosquitoes identified to species"="Response")
cbind(Country=data$SI01, q29, q30, q31) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()
```

<br>
 
#### Minimum infection rate (MIR) calculations for any _Aedes_-borne arboviruses (ref Q32)

```{r}
responses <- get_responses("32")
colnames( responses ) <- c("Response", "Comments")
cbind(Country=data$SI01, responses) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()
```

<br> 

#### Laboratories testing mosquito pools for arboviruses (ref Q33)

```{r}
responses <- get_responses("33") 
# other <- responses %>% select(Other)
# responses <- responses %>% select(-Other)

responses <- responses %>%
  mutate_at( .vars=vars(colnames(responses)),
             .funs = forcats::fct_recode,
             "X" = "Yes",
             " " = "Not selected") 

empty_cols = c()
for(i in 1:ncol(responses)){
  responses[,i] <- as.character( responses[,i] )
  responses[ which( is.na( responses[,i])) ,i] <- " "
  if( all(responses[,i] != "X" )){
    empty_cols = c(empty_cols, colnames(responses)[i])
  }
}

cbind(Country=data$SI01, responses) %>%
  select(-empty_cols) %>% 
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  autofit()
```
