---
title: ' '
pagetitle: 'EURO Q35'
output:
  html_document:
    includes:
      in_header: EURO_Q35_header.html
params:
  region: EURO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{js}
// Region dropdown
/* When the user clicks on the button,
toggle between hiding and showing the dropdown content */
function myFunction() {
  document.getElementById("myDropdown").classList.toggle("show");
}

// Close the dropdown menu if the user clicks outside of it
window.onclick = function(event) {
  if (!event.target.matches('.dropbtn')) {
    var dropdowns = document.getElementsByClassName("dropdown-content");
    var i;
    for (i = 0; i < dropdowns.length; i++) {
      var openDropdown = dropdowns[i];
      if (openDropdown.classList.contains('show')) {
        openDropdown.classList.remove('show');
      }
    }
  }
}
// end region dropdown

element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Overview of data  */
    var overview_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        overview_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }
    
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true) {
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    /* #regional-navigation-disease-surveillance  */
    var regional_menu_opened = $('#regional-navigation-disease-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-disease-surveillance').length &&
        !$(e.target).is('#regional-navigation-disease-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-disease-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-lab-capacity  */
    var regional_menu_opened = $('#regional-navigation-lab-capacity').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-lab-capacity').length &&
        !$(e.target).is('#regional-navigation-lab-capacity') &&
        regional_menu_opened === true) {
            $('#regional-navigation-lab-capacity').collapse('toggle');
    }
    
    /* #regional-navigation-management  */
    var regional_menu_opened = $('#regional-navigation-management').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-management').length &&
        !$(e.target).is('#regional-navigation-management') &&
        regional_menu_opened === true) {
            $('#regional-navigation-management').collapse('toggle');
    }
    
    /* #regional-navigation-vector-surveillance  */
    var regional_menu_opened = $('#regional-navigation-vector-surveillance').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-vector-surveillance').length &&
        !$(e.target).is('#regional-navigation-vector-surveillance') &&
        regional_menu_opened === true) {
            $('#regional-navigation-vector-surveillance').collapse('toggle');
    }
    
    /* #regional-navigation-community  */
    var regional_menu_opened = $('#regional-navigation-community').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-community').length &&
        !$(e.target).is('#regional-navigation-community') &&
        regional_menu_opened === true) {
            $('#regional-navigation-community').collapse('toggle');
    }
    
    /* #regional-navigation-preparedness  */
    var regional_menu_opened = $('#regional-navigation-preparedness').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-preparedness').length &&
        !$(e.target).is('#regional-navigation-preparedness') &&
        regional_menu_opened === true) {
            $('#regional-navigation-preparedness').collapse('toggle');
    }
    
    /* #regional-navigation-surveillance-staffing  */
    var regional_menu_opened = $('#regional-navigation-surveillance-staffing').hasClass('in');
    if(!$(e.target).closest('#regional-navigation-surveillance-staffing').length &&
        !$(e.target).is('#regional-navigation-surveillance-staffing') &&
        regional_menu_opened === true) {
            $('#regional-navigation-surveillance-staffing').collapse('toggle');
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }

});

```

```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
region_countries <- load_regions_countries()
```

```{r}
data <- data %>% filter(Region==params$region) %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

```{r}
amro <- params$region == "AMRO"
```


```{r}
responses <- get_responses("35")
other <- responses %>% select(Other)
responses <- responses %>% select(-Other)

responses <- responses %>%
  mutate( across(everything(),
                 ~replace_na(.x, " "))) %>%
  mutate( across(everything(), 
                 recode_factor, 
                 "Yes" = "X", 
                 "Not selected" = " ")) %>%
  mutate( across(everything(),
                 as.character)) %>%
  rename("Adulticiding"="Adulticiding (insecticide application against adult mosquitoes)")

empty_cols = c()
for(i in 1:ncol(responses)){
  if( all(responses[,i] == " " )){
    empty_cols = c(empty_cols, colnames(responses)[i])
  }
}

if( any(!is.na(other$Other))){
  responses <- cbind( responses, other)
}

ft35 <- cbind(Country=data$SI01, responses) %>%
  select(-empty_cols) %>%
  regulartable() %>%
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( align="center", part="all" ) %>%
  align( j=1, align="left", part="all") %>%
  valign( valign = "top", part="header" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()
idx <- which( ft35$col_keys == "Wolbachia method")
if( length(idx) > 0 ){
  ft35 <- ft35 %>% compose( j=idx, part="header", value = as_paragraph(as_i("Wolbachia"), " method"))
}

empty_cols <- empty_cols[ which(empty_cols != "None")]

if( length(empty_cols) > 0 ){
  empty_cols <- paste0("No countries reported the use of _", paste0(empty_cols, collapse="_, _"), "_.")
} else{
  empty_cols <- " "
}

responses <- get_responses("35c")
ft35c <- cbind(Country=data$SI01, responses) %>%
  drop_na( Response ) %>%
  rename("Product used"=Response) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  valign( valign = "top", part="header" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

responses <- get_responses("39")
responses <- cbind(Country=data$SI01, responses) 
monitoring <- responses$Country[ which(responses$Response == "Yes")]

responses <- get_responses("36")
ft36 <- cbind(Country=data$SI01, responses) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  valign( valign = "top", part="header" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

ft_width <- max( c( flextable_dim(ft35)$widths, flextable_dim(ft35c)$widths, flextable_dim(ft36)$widths ))

ft35 <- ft35 %>% width( width=ft_width)
ft35c <- ft35c %>% width( width=ft_width)
ft36 <- ft36 %>% width( width=ft_width)
```

### Vector control methods

#### Vector control methods used in local jurisdictions in the past two years (either using government staff and resources, or subcontracting to a different entity to do so) (ref Q35)

```{r}
ft35
```

`r empty_cols`

<br>

#### Adulticides and/or larvicides (brand and product name) used (ref Q35c)

```{r}
ft35c
```

<br>

#### Surveillance system in place for monitoring _Aedes_ resistance to the insecticide(s) used (ref Q39)

`r monitoring` indicated that there is _Aedes_ resistance monitoring in place. 

<br> 

#### Staff training in vector control and surveillance (ref Q36)

```{r eval=!amro}
ft36 
```

```{r eval = amro}
disclaimer <- "#### Question 36 was not included in the dataset shared with AMRO for completion. Please see the Arbovirus Survey Overview for more information."
```

<br>

`r if(amro){ disclaimer }`
