---
title: "Regional epidemiological risk data"
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
ggplot2::theme_set(ggplot2::theme_bw())

# options(scipen = '999')
```

```{js}
element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true){
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }


});

```


```{r, child="_sessioninfo.Rmd"}
```

```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
df <- load_data()
```

## Vectors present and level of risk 

#### Is there a record of _Aedes aegypti_ or _Aedes albopictus_ being found in your country in the past 5 years? Please choose only one of the following (Question 34) 

```{r}

# relevant question: q34

responses <- get_responses("34")
qdf <- data.frame(Region = df$Region, Response = responses) %>% 
  drop_na(Region) %>% 
  mutate( Response = factor( replace_na( as.character(Response), "Unanswered"))) %>%
  mutate( Response = recode_factor(Response, 
                                 "Yes, both Aedes aegypti and Aedes albopictus" = "Both Aedes aegypti and Aedes albopictus",
                                 "Yes, only Aedes aegypti" = "Only Aedes aegypti",
                                 "Yes, only Aedes albopictus" = "Only Aedes albopictus",
                                 "Unknown within the country at this time" = "Unknown at this time",
                                 "None found in the country at this time" = "None found at this time",
                                 "Unanswered" = "Unanswered")) %>% 
  group_by(Region, Response) %>%
  tally 
qdf %>% 
  pivot_wider(names_from=Response, values_from=n, names_sort=TRUE) %>%
  mutate( across( everything(), ~ replace_na(.x, 0))) %>% 
  adorn_totals() %>%
  regulartable() %>%
  hline(i=4) %>%
  autofit 

```

#### Please describe the potential public health threat from _Aedes aegypti_ in your country. (Question 34b) 

```{r}

# relevant question: q34b

responses <- get_responses("34b") %>%
  select(-Other) 
qdf <- data.frame(Region = df$Region, Response = responses$`Please choose only one of the following:`) %>% 
  drop_na(Region) %>% 
  mutate( Response = factor( replace_na( as.character(Response), "Unanswered"))) %>%
  group_by(Region, Response) %>%
  tally 
qdf %>% 
  pivot_wider(names_from=Response, values_from=n, names_sort=TRUE) %>%
  mutate( across( everything(), ~ replace_na(.x, 0))) %>% 
  adorn_totals() %>%
  regulartable() %>%
  hline(i=4) %>%
  autofit 

```

#### Please describe the potential public health threat from _Aedes albopictus_ in your country. (Question 34c) 

```{r}

# relevant question: q34c

responses <- get_responses("34c") %>%
  select(-Other) 
qdf <- data.frame(Region = df$Region, Response = responses$`Please choose only one of the following:`) %>% 
  drop_na(Region) %>% 
  mutate( Response = factor( replace_na( as.character(Response), "Unanswered"))) %>%
  group_by(Region, Response) %>%
  tally 
qdf %>% 
  pivot_wider(names_from=Response, values_from=n, names_sort=TRUE) %>%
  mutate( across( everything(), ~ replace_na(.x, 0))) %>% 
  adorn_totals() %>%
  regulartable() %>%
  hline(i=4) %>%
  autofit 

```
