---
title: "Regional surveillance capacity indicators"
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
ggplot2::theme_set(ggplot2::theme_bw())

# options(scipen = '999')
```

```{js}
element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Global data  */
    var global_menu_opened = $('#global-navigation').hasClass('in');
    if(!$(e.target).closest('#global-navigation').length &&
        !$(e.target).is('#global-navigation') &&
        global_menu_opened === true){
            $('#global-navigation').collapse('toggle');
            $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#global-navigation').attr('aria-expanded') === "false") {
      $( "#Global-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#global-navigation').attr('aria-expanded') === "true") {
      $( "#Global-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true){
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }


});

```


```{r, child="_sessioninfo.Rmd"}
```

```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
df <- load_data()
```

## Conducting surveillance on humans

#### In the last 2 years, did your country conduct national epidemiological surveillance for human cases of arboviral disease? (Question 12) 

```{r}

# relevant question: q12 (surveillance on humans)

responses <- get_responses("12") 
qdf <- data.frame(Region = df$Region, Response = responses) %>% 
  drop_na(Region) %>% 
  mutate( Response = factor( replace_na( as.character(Response), "Unanswered"))) %>% 
  mutate( Response = fct_relevel(Response, "Yes", "No", "I don't know", "Unanswered")) %>% 
  group_by(Region, Response) %>% 
  tally %>% 
  pivot_wider(names_from=Response, values_from=n) %>%
  adorn_totals()
regulartable(qdf) %>%
  colformat_num( na_str="0" ) %>%
  hline(i=4) %>%
  autofit 

```

## Conducting surveillance on vectors 

#### For the last 2 years, did your country conduct entomologic surveillance for arboviral infections in mosquito vectors? (Question 28) 

```{r}
# relevant question: q28 (surveillance on vectors)

responses <- get_responses("28")
qdf <- data.frame(Region = df$Region, Response = responses) %>% 
  drop_na(Region) %>% 
  mutate( Response = factor( replace_na( as.character(Response), "Unanswered"))) %>% 
  mutate( Response = fct_relevel(Response, "Yes", "No", "Don't know", "Unanswered")) %>% 
  group_by(Region, Response) %>% 
  tally %>% 
  pivot_wider(names_from=Response, values_from=n) %>%
  adorn_totals()
regulartable( qdf ) %>%
  colformat_num( na_str="0" ) %>%
  hline(i=4) %>% 
  autofit 

```


## Conducting surveillance on animals 

#### During the last 2 years, did your country conduct national epidemiological surveillance for arboviral disease in animals (e.g., epizootic surveillance for yellow fever in endemic areas)? (Question 41) 

```{r}

# relevant question: q41 (surveillance on animals)

responses <- get_responses("41")
qdf <- data.frame(Region = df$Region, Response = responses) %>% 
  drop_na(Region) %>% 
  mutate( Response = factor( replace_na( as.character(Response), "Unanswered"))) %>% 
  mutate( Response = fct_relevel(Response, "Yes", "No", "I don't know", "Unanswered")) %>%
  group_by(Region, Response) %>% 
  tally %>% 
  pivot_wider(names_from=Response, values_from=n) %>%
  adorn_totals()
regulartable( qdf ) %>%
  colformat_num( na_str="0" ) %>%
  hline(i=4) %>% 
  autofit 

```
