
### Vector surveillance and control

#### Countries conducting mosquito surveillance, by stage and species identification (ref Q29, 30, 31)

```{r}
q29 <- get_responses("29")
q29 <- cbind( Region = data$Region, q29 )
nums <- q29 %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
q29 <- q29 %>% 
  filter( Response == "Yes" ) %>% 
  group_by( Region)  %>%
  tally() %>%
  right_join( nums, by="Region") %>%
  replace_na( list(n = 0)) %>%
  mutate( Percentage = paste0( "(", round( 100*n/n_countries), "%)" )) %>%
  select(Region, n, Percentage) %>%
  unite( "Adult surveillance", n:Percentage, sep=" " )

q30 <- get_responses("30")
q30 <- cbind( Region = data$Region, q30 )
nums <- q30 %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
q30 <- q30 %>% 
  filter( Response == "Yes" ) %>% 
  group_by( Region)  %>%
  tally() %>%
  right_join( nums, by="Region") %>%
  replace_na( list(n = 0)) %>%
  mutate( Percentage = paste0( "(", round( 100*n/n_countries), "%)" )) %>%
  select(Region, n, Percentage) %>%
  unite( "Larval/pupal surveillance", n:Percentage, sep=" " )

q31 <- get_responses("31")
q31 <- cbind( Region = data$Region, q31 )
nums <- q31 %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
q31 <- q31 %>% 
  filter( Response == "Yes" ) %>% 
  group_by( Region)  %>%
  tally() %>%
  right_join( nums, by="Region") %>%
  replace_na( list(n = 0)) %>%
  mutate( Percentage = paste0( "(", round( 100*n/n_countries), "%)" )) %>%
  select(Region, n, Percentage) %>%
  unite( "Trapped mosquitoes identified to species", n:Percentage, sep=" " )

left_join( q29, q30, by="Region") %>%
  left_join( q31, by="Region") %>%
  rename("Regional office" = Region ) %>%
  regulartable() %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( j=2:4, align="center", part="all" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit()

```

<br>

#### Vector control methods used in local jurisdictions in the past two years (either using government staff and resources, or subcontracting to a different entity to do so) (ref Q35)

```{r}
responses <- get_responses("35")
responses <- cbind( Region = data$Region, responses) %>% 
  drop_na(Region) 
nums <- responses %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
other <- responses %>% select(Other)

responses %>% 
  select(-Other) %>% 
  mutate( across(!Region, ~ ifelse(.x == "Yes", 1, 0))) %>%
  group_by(Region) %>%
  summarize( across(everything(), ~ sum(.x, na.rm=TRUE))) %>%
  ungroup() %>%
  left_join( nums, by="Region") %>%
  group_by(Region) %>%
  mutate( across( everything(), ~ paste0( .x, " (", round(100*(.x)/n_countries), "%)") ) ) %>%
  select(-n_countries) %>%
  rename("Regional office" = Region,
         "Adulticiding"="Adulticiding (insecticide application against adult mosquitoes)",
         "Insect growth regulators" = "Insect growth regulators (eg , pyriproxyfen)") %>%
  regulartable %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( j=2:7, align="center", part="all" ) %>%
  compose( j=5, part="header", value = as_paragraph(as_i("Wolbachia"), " method")) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit() 

```

<br>

#### Vector indices measured and calculation of infection rates (ref Q37b)

```{r}
responses <- get_responses("37b")
responses <- cbind( Region = data$Region, responses) %>% 
  drop_na(Region) 
nums <- responses %>% 
  group_by( Region ) %>%
  tally(name = "n_countries")
other <- responses %>% select(Other)
responses %>% 
  select(-Other) %>% 
  mutate( across(!Region, ~ ifelse(.x == "Yes", 1, 0))) %>%
  group_by(Region) %>%
  summarize( across(everything(), ~ sum(.x, na.rm=TRUE))) %>%
  ungroup() %>%
  left_join( nums, by="Region") %>%
  group_by(Region) %>%
  mutate( across( everything(), ~ paste0( .x, " (", round(100*(.x)/n_countries), "%)") ) ) %>%
  select(-n_countries) %>%
  rename("Regional office" = Region ) %>%
  regulartable %>% 
  theme_zebra(odd_header="#048ECA", odd_body = "#D6EAF8") %>% 
  color( color="#FFFFFF", part="header" ) %>% 
  align( j=2:7, align="center", part="all" ) %>%
  padding( padding.top = 10, part="all") %>%
  padding( padding.bottom = 10, part="all") %>%
  autofit() 
```
