---
title: ' '
pagetitle: 'ALL national'
output:
  html_document:
    includes:
      in_header: ALL_national_header.html
params:
  region: ALL
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
ggplot2::theme_set(ggplot2::theme_bw())

# options(scipen = '999')
```


```{js}
element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Global data  */
    var global_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        global_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true){
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }


});

```


```{css, echo=FALSE}
h4 {
  text-align: center;
}
```


```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
```


Available reports: 

<ul>
<li><a href="country_reports/Afghanistan.pdf" style="color:#048eca;">Afghanistan</a></li>
<li><a href="country_reports/Albania.pdf" style="color:#048eca;">Albania</a></li>
<li><a href="country_reports/Armenia.pdf" style="color:#048eca;">Armenia</a></li>
<li><a href="country_reports/Bahrain.pdf" style="color:#048eca;">Bahrain</a></li>
<li><a href="country_reports/Bangladesh.pdf" style="color:#048eca;">Bangladesh</a></li>
<li><a href="country_reports/Bhutan.pdf" style="color:#048eca;">Bhutan</a></li>
<li><a href="country_reports/Bosnia and Herzegovina.pdf" style="color:#048eca;">Bosnia and Herzegovina</a></li>
<li><a href="country_reports/Bulgaria.pdf" style="color:#048eca;">Bulgaria</a></li>
<li><a href="country_reports/Cambodia.pdf" style="color:#048eca;">Cambodia</a></li>
<li><a href="country_reports/China.pdf" style="color:#048eca;">China</a></li>
<li><a href="country_reports/Croatia.pdf" style="color:#048eca;">Croatia</a></li>
<li><a href="country_reports/Egypt.pdf" style="color:#048eca;">Egypt</a></li>
<li><a href="country_reports/France.pdf" style="color:#048eca;">France</a></li>
<li><a href="country_reports/Georgia.pdf" style="color:#048eca;">Georgia</a></li>
<li><a href="country_reports/Germany.pdf" style="color:#048eca;">Germany</a></li>
<li><a href="country_reports/Greece.pdf" style="color:#048eca;">Greece</a></li>
<li><a href="country_reports/Hungary.pdf" style="color:#048eca;">Hungary</a></li>
<li><a href="country_reports/India.pdf" style="color:#048eca;">India</a></li>
<li><a href="country_reports/Indonesia.pdf" style="color:#048eca;">Indonesia</a></li>
<li><a href="country_reports/Iraq.pdf" style="color:#048eca;">Iraq</a></li>
<li><a href="country_reports/Italy.pdf" style="color:#048eca;">Italy</a></li>
<li><a href="country_reports/Jordan.pdf" style="color:#048eca;">Jordan</a></li>
<li><a href="country_reports/Kiribati.pdf" style="color:#048eca;">Kiribati</a></li>
<li><a href="country_reports/Lao People's Democratic Republic.pdf" style="color:#048eca;">Lao People's Democratic Republic</a></li>
<li><a href="country_reports/Libya.pdf" style="color:#048eca;">Libya</a></li>
<li><a href="country_reports/Malaysia.pdf" style="color:#048eca;">Malaysia</a></li>
<li><a href="country_reports/Maldives.pdf" style="color:#048eca;">Maldives</a></li>
<li><a href="country_reports/Malta.pdf" style="color:#048eca;">Malta</a></li>
<li><a href="country_reports/Monaco.pdf" style="color:#048eca;">Monaco</a></li>
<li><a href="country_reports/Myanmar.pdf" style="color:#048eca;">Myanmar</a></li>
<li><a href="country_reports/Nauru.pdf" style="color:#048eca;">Nauru</a></li>
<li><a href="country_reports/Nepal.pdf" style="color:#048eca;">Nepal</a></li>
<li><a href="country_reports/Oman.pdf" style="color:#048eca;">Oman</a></li>
<li><a href="country_reports/Pakistan.pdf" style="color:#048eca;">Pakistan</a></li>
<li><a href="country_reports/Papua New Guinea.pdf" style="color:#048eca;">Papua New Guinea</a></li>
<li><a href="country_reports/Philippines.pdf" style="color:#048eca;">Philippines</a></li>
<li><a href="country_reports/Portugal.pdf" style="color:#048eca;">Portugal</a></li>
<li><a href="country_reports/Qatar.pdf" style="color:#048eca;">Qatar</a></li>
<li><a href="country_reports/Romania.pdf" style="color:#048eca;">Romania</a></li>
<li><a href="country_reports/San Marino.pdf" style="color:#048eca;">San Marino</a></li>
<li><a href="country_reports/Saudi Arabia.pdf" style="color:#048eca;">Saudi Arabia</a></li>
<li><a href="country_reports/Singapore.pdf" style="color:#048eca;">Singapore</a></li>
<li><a href="country_reports/Slovenia.pdf" style="color:#048eca;">Slovenia</a></li>
<li><a href="country_reports/Somalia.pdf" style="color:#048eca;">Somalia</a></li>
<li><a href="country_reports/Spain.pdf" style="color:#048eca;">Spain</a></li>
<li><a href="country_reports/Sudan.pdf" style="color:#048eca;">Sudan</a></li>
<li><a href="country_reports/Switzerland.pdf" style="color:#048eca;">Switzerland</a></li>
<li><a href="country_reports/Syrian Arab Republic.pdf" style="color:#048eca;">Syrian Arab Republic</a></li>
<li><a href="country_reports/Thailand.pdf" style="color:#048eca;">Thailand</a></li>
<li><a href="country_reports/Tunisia.pdf" style="color:#048eca;">Tunisia</a></li>
<li><a href="country_reports/Turkey.pdf" style="color:#048eca;">Turkey</a></li>
<li><a href="country_reports/Vanuatu.pdf" style="color:#048eca;">Vanuatu</a></li>
<li><a href="country_reports/Viet Nam.pdf" style="color:#048eca;">Viet Nam</a></li>
<li><a href="country_reports/Yemen.pdf" style="color:#048eca;">Yemen</a></li>
</ul>
