---
title: ' '
pagetitle: 'EMRO Q35'
output:
  html_document:
    includes:
      in_header: EMRO_Q35_header.html
params:
  region: EMRO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
ggplot2::theme_set(ggplot2::theme_bw())

# options(scipen = '999')
```


```{js}
element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Global data  */
    var global_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        global_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true){
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }


});

```


```{css, echo=FALSE}
h4 {
  text-align: center;
}
```


```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
```


```{r}
data <- data %>% filter(Region==params$region) %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

### Vector control methods

<br>

#### Vector control methods used in local jurisdictions in the past two years (either using government staff and resources, or subcontracting to a different entity to do so) (ref Q35)

```{r}
responses <- get_responses("35")
other <- responses %>% select(Other)
responses <- responses %>% select(-Other)

responses <- responses %>%
  mutate_at( .vars=vars(colnames(responses)),
             .funs = forcats::fct_recode,
             "X" = "Yes",
             " " = "Not selected") %>%
  rename("Adulticiding"="Adulticiding (insecticide application against adult mosquitoes)")

empty_cols = c()
for(i in 1:ncol(responses)){
  responses[,i] <- as.character( responses[,i] )
  responses[ which( is.na( responses[,i])) ,i] <- " "
  if( all(responses[,i] != "X" )){
    empty_cols = c(empty_cols, colnames(responses)[i])
  }
}

if( any(!is.na(other$Other))){
  responses <- cbind( responses, other)
}

cbind(Country=data$SI01, responses) %>%
  select(-empty_cols) %>%
  regulartable() %>%
  set_caption(caption) %>% autofit()

empty_cols <- empty_cols[ which(empty_cols != "None")]

```

No countries reported the use of `r (empty_cols)`.

<br>

#### Adulticides and/or larvicides (brand and product name) used (ref Q35c)

```{r}
responses <- get_responses("35c")
cbind(Country=data$SI01, responses) %>%
  drop_na( Response ) %>%
  rename("Product used"=Response) %>%
  regulartable() %>% autofit()
```

<br>

#### Surveillance system in place for monitoring _Aedes_ resistance to the insecticide(s) used (ref Q39)

```{r}
responses <- get_responses("39")
responses <- cbind(Country=data$SI01, responses) 
monitoring <- responses$Country[ which(responses$Response == "Yes")]
```

`r monitoring` indicated that there is _Aedes_ resistance monitoring in place. 

<br> 

#### Staff training in vector control and surveillance (ref Q36)

```{r}
responses <- get_responses("36")
cbind(Country=data$SI01, responses) %>%
  regulartable() %>% autofit()
```
