---
title: ' '
pagetitle: 'PAHO Q43'
output:
  html_document:
    includes:
      in_header: PAHO_Q43_header.html
params:
  region: PAHO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
ggplot2::theme_set(ggplot2::theme_bw())

# options(scipen = '999')
```


```{js}
element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Global data  */
    var global_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        global_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true){
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }


});

```


```{css, echo=FALSE}
h4 {
  text-align: center;
}
```


```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
```


```{r}
data <- data %>% filter(Region==params$region) %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

### Presence of a community outreach program that also covers arboviral diseases

<br>

#### Community outreach program presence, leadership, and geographic scope (ref Q43, 43b, 43c)

```{r}
q43 <- get_responses("43") %>%
  rename( "In place" = Response)

q43b <- get_responses("43b") %>%
  rename( "Entity in charge" = Response)

q43c <- get_responses("43c") 
colnames( q43c ) <- c("Response","Areas") 
q43c <- q43c %>% 
  mutate( across( everything(), as.character)) %>%
  mutate( across( everything(), replace_na, "") )
q43c$Response[ grep("Only selected areas", q43c$Response ) ] <- "Only selected areas"
q43c <- q43c %>%
  unite( Scope, Response:Areas, sep="\n")

cbind(Country=data$SI01, q43, q43b, q43c) %>%
  regulartable() %>% autofit()

```

<br>

#### Is the community outreach/social mobilization program sufficiently funded to cover staff time, prevention and outreach activities as needed? (ref Q43d)

```{r}
responses <- get_responses("43d")
cbind(Country=data$SI01, responses) %>%
  regulartable() %>%
  hline( part="all") # %>% autofit()
```

<br>

#### Resources needed to ensure adequate community outreach capacity (ref Q43e)

```{r}
responses <- get_responses("43e")
other <- responses %>% select(Other)
responses <- responses %>% select(-Other)

responses <- responses %>%
  mutate( across(everything(), na_if, "Not selected") ) %>%
  mutate( across(everything(), as.character)) %>%
  mutate( across(everything(), str_replace, pattern="Yes", replacement="X"))

keep_cols = c()
for(i in 1:ncol(responses)){
  if( any( !is.na(responses[,i]) )){
    keep_cols = c(keep_cols, colnames(responses)[i])
  }
}

if( any(!is.na(other$Other))){
  responses <- cbind( responses, other)
  keep_cols <- c( keep_cols, "Other")
}

cbind(Country=data$SI01, responses) %>%
  select( c("Country", keep_cols )) %>%
  filter( if_any(keep_cols, ~ !is.na(.) ) ) %>%
  regulartable() %>% autofit()

```

<br>

#### Regular training sessions for staff in charge of community sensitization, mobilisation and acceptance of interventions dedicated to control arboviral diseases (ref Q45)

```{r}
responses <- get_responses("45")
colnames( responses ) <- c("Response", "Comments")
cbind(Country=data$SI01, responses) %>%
  # mutate( Response = factor( replace_na( as.character(Response), "Unanswered"))) %>%
  mutate( Response = recode_factor(.x = Response,
                                   "Yes. If yes, please describe in comments field:"="Yes",
                                   "No"="No",
                                   "I don’t know"="I don’t know")) %>%
  regulartable() %>% autofit()
```
