---
title: ' '
pagetitle: 'PAHO Q21'
output:
  html_document:
    includes:
      in_header: PAHO_Q21_header.html
params:
  region: PAHO
---

```{r, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
ggplot2::theme_set(ggplot2::theme_bw())

# options(scipen = '999')
```


```{js}
element = document.getElementById('WHO_logo');
console.log(element)

$('#WHO_logo').click(function(e){
    console.log("Exists!")
});


window.onscroll = function() { scrollFunction() };

var navbar = document.getElementById("navbar");
var logoWhiteElement = document.getElementById("whiteLogoPosition")
var sticky = navbar.offsetTop;

function scrollFunction() {
  if (window.pageYOffset >= sticky) {
    navbar.classList.add("sticky");
    logoWhiteElement.classList.add("white_logo_appear");
  } else {
    navbar.classList.remove("sticky");
    logoWhiteElement.classList.remove("white_logo_appear");
  }
}

$(document).on('click', function (e){
    /* Global data  */
    var global_menu_opened = $('#overview-navigation').hasClass('in');
    if(!$(e.target).closest('#overview-navigation').length &&
        !$(e.target).is('#overview-navigation') &&
        global_menu_opened === true){
            $('#overview-navigation').collapse('toggle');
            $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#overview-navigation').attr('aria-expanded') === "false") {
      $( "#Overview-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#overview-navigation').attr('aria-expanded') === "true") {
      $( "#Overview-Li-area" ).addClass("activeMenuState");
    }

     /* Regional data  */
    var regional_menu_opened = $('#regional-navigation').hasClass('in');
    if(!$(e.target).closest('#regional-navigation').length &&
        !$(e.target).is('#regional-navigation') &&
        regional_menu_opened === true){
            $('#regional-navigation').collapse('toggle');
            $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#regional-navigation').attr('aria-expanded') === "false") {
      $( "#Regional-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#regional-navigation').attr('aria-expanded') === "true") {
      $( "#Regional-Li-area" ).addClass("activeMenuState");
    }
     
     
     /* Country data  */
    var country_menu_opened = $('#country-navigation').hasClass('in');
    if(!$(e.target).closest('#country-navigation').length &&
        !$(e.target).is('#country-navigation') &&
        country_menu_opened === true){
            $('#country-navigation').collapse('toggle');
            $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    
    if ($('#country-navigation').attr('aria-expanded') === "false") {
      $( "#Country-Li-area" ).removeClass("activeMenuState");
    }
    if ($('#country-navigation').attr('aria-expanded') === "true") {
      $( "#Country-Li-area" ).addClass("activeMenuState");
    }


});

```


```{css, echo=FALSE}
h4 {
  text-align: center;
}
```


```{r, echo = FALSE}
source('functions.R')
dict <- load_dict()
data <- load_data()
```


```{r}
data <- data %>% filter(Region==params$region) %>% droplevels() %>% mutate(SI01 = as.character(SI01)) %>% arrange( SI01 )
```

#### Countries with clinical guidelines for healthcare workers on diagnosis and clinical management of cases and severe cases of _Aedes_-borne arboviral diseases (ref Q21)

```{r}
responses <- get_responses("21")
responses <- cbind(Country=data$SI01, responses) 

available <- responses$Country[which(responses$Response == "Yes")]
no_answer <- responses$Country[which(is.na(responses$Response))]
no_guidelines <- responses$Country[which(responses$Response == "No")]

```

The following countries indicated availability of clinical guidelines: `r available`.

`r no_answer` did not answer the question and `r no_guidelines` indicated no guidelines. 

<br> 

#### Training for healthcare workers on clinical diagnosis and management of _Aedes_-borne arboviral diseases (ref Q24)

```{r}
responses <- get_responses("24")
colnames(responses) <- c("Response","Training")
cbind(Country=data$SI01, responses) %>%
  mutate( Response = recode_factor(.x = Response,
                                   "Yes, specific training is provided. If so, please specify:"="X",
                                   "No"=" ")) %>%
  filter(Response=="X") %>% 
  select(-Response) %>%
  replace_na( list(Training="Not specified")) %>%
  regulartable() %>% autofit()

```
